---
title: "Exam3"
author: "Taeyoung Lee"
date: "7/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions

1. Clear the environment. 

```{r}
# clear the environment
rm(list=ls())
```


2.Use thetidycensuspackage to 
(a) find the inequality Gini index variable explained on the last exam, 
(b) import in the state-level inequality Gini estimates for 2010 and 2015 in the five-year American Community Survey as a single panel dataset; 
(c) rename estimate as gini in your final data frame, which you should call inequality_panel;
(d) rename NAME to state as well; 
(e) ensure that inequality_panel has a year variable so we can distinguish between the 2010 and 2015 giniindex data; 
(f) as afinal step, run the head()command so we can get a quick peak a tinequality_panel(Hint: you may need to import each year separately and then append the two dataframes together.) [15 points]


```{r}
# load the library
library(tidycensus)

# Load API key
census_api_key("09f87f16af7fdb0ddb78d0416c83755f7580f03b",
               install = TRUE,
               overwrite = TRUE)

# import 2010 and 2015 data from acs5
acs_2010 <- load_variables(year = 2010, "acs5")
acs_2015 <- load_variables(year = 2015, "acs5")

# subsetting gini index
gini_2010 <- get_acs(geography = "state",
                     variables = c(gini = c("B19083_001")),
                     year = 2010)

gini_2015 <-get_acs(geography = "state",
                     variables = c(gini = c("B19083_001")),
                     year = 2015)


# Create a single panel data frame --gini_data

# First, load the libraries
library(bit64)
library(tidyverse)

# second, create "year" variables
gini_2010$year <- 2010
gini_2015$year <- 2015

# bind the dfs
inequality_panel <- bind_rows(gini_2010, gini_2015)
  
# Rename estimate to gini
library(data.table)
setnames(inequality_panel,"estimate", "gini")  

# Rename NAME to state
setnames(inequality_panel,"NAME", "state")  

# Remove gini variable
inequality_panel$variable = NULL

# take a quick peak
head(inequality_panel)
```


3. Reshape the inequality_panel wide, such that the ginivalues for 2010 and 2015 have their own columns. Also, please keep both the state and GEOID variables. Call the resulting data frame inequality_wide. 
After you are done with the reshape, runthe head() command so we can get a quick peak at the data. [5 points]

```{r}

# Pivot the data frame wide by ginivalues

inequality_wide <-
inequality_panel %>%
pivot_wider(id_cols = c("GEOID", "state", "year"), 
            names_from = "year", 
            values_from = "gini",
            names_prefix = "gini_")

# Take a quick peak
head(inequality_wide)
```

4. Reshape inequality_wide to long format. Once you are done, run the head() com-mand so we can get a quick peak at the data. [5 points]

```{r}

# Reshape the datafrime to long format
inequality_long <-
  inequality_wide %>%
  pivot_longer(cols = starts_with(c("gini_2010", "gini_2015")), 
                names_to ="year", 
                names_prefix = "gini_", 
                values_to = "gini", 
                values_drop_na = FALSE) %>% 
                filter(!(gini==0))


# Take a quick peak
head(inequality_long)
```


5.Show with some Rcode that inequality_panel and inequality_long have the same number of observations. [5 points]


```{r}
str(inequality_panel)
str(inequality_long)

```


6. Collapse the inequality_long data frame by state, such that you obtain a single mean giniscore for each state for the years 2010 and 2015. When collapsing, also keep both the GEOID and state variables. Call your resulting data frame inequality_collapsed.[5 points]

```{r}

# Collapse the data to mean giniscore by state
inequality_collapsed <-
  inequality_long %>%
  group_by(GEOID, state) %>% 
  summarize(across(where(is.numeric), mean)) 


```


7.Produce a map of the United States that colors in the state polygons by their mean gini scores from inequality_collapsed, using the WGS84 coordinate system. When doing so, use the viridis color scheme. 


```{r}
# Load the pacakages
library(rio)
library(tidyverse)
library(googlesheets4)
library(labelled)
library(data.table)
library(varhandle)
library(ggrepel)
library(geosphere)
library(rgeos)
library(viridis)
library(mapview)
library(rnaturalearth)
library(rnaturalearthdata)
library(devtools) 
library(remotes)
library(rnaturalearthhires) #devtools:: install_github("ropensci/rnaturalearthhires")
library(raster) 
library(sp)
library(sf)
library(ggsflabel) #  devtools:: install_github("yutannihilation/ggsflabel")
library(Imap) # nice mapping / color function


# Load the us map
us <- ne_countries(country = 'United States of America', scale = "medium", returnclass = "sf")

# Rename
setnames(inequality_collapsed, "gini", "mean gini score")

# Create the map
us_map = ggplot() +
  geom_sf(data = us) +
  geom_sf(data = inequality_collapsed, aes(fill = "mean gini score")) +
  scale_fill_viridis(option = "viridis") +
  ggtitle("Mean Gini Score for 2010 and 2015") +
theme(plot.title = element_text(hjust = 0.5)) +
theme_void()
  
```


8. Use the WDI package to import in data on Gross Domestic Product (GDP) in current US dollars. When doing so, include all countries and only the years 2006 and 2007.
Rename your GDP variable to gdp_current. [5 points]

```{r}
# Load the library
library(WDI)

# https://data.worldbank.org/indicator/NY.GDP.MKTP.CD
gdp_current = WDI(country = "all", indicator = c("NY.GDP.MKTP.CD"),
                    start = 2006, 
                    end = 2007, 
                    extra = FALSE, cache = NULL)
View (gdp_current)


# rename variables so they are understandable 
library(data.table)
setnames(gdp_current,"NY.GDP.MKTP.CD", "gdp_current")
```


9. Deflate gdp_current to constant 2010 or 2015 US dollars, and call the new variable gdp_deflated. In words, also tell us the base year that you picked and why. At the end, run a head() command to prove that everything works. [5 points]

```{r}

# Google "GDP deflator World Bank"
# https://data.worldbank.org/indicator/NY.GDP.DEFL.ZS
gdp_deflated = WDI(country = "all", indicator = c("NY.GDP.DEFL.ZS"),
start = 2006, 
end = 2015, 
extra = FALSE, cache = NULL)


head(gdp_deflated)
```

why? 

I picked up 2015 because 2010 would be affected by 2008 crisis so it would be distorted.


10.In a Shiny app, what are the three main components and their subcomponents? [5points]
Main
1. UI         (1) input (2) output
2. server     (1) input (2) output
3. (execute the) shinyApp   (1) UI (2) server


11. Pull this.pdf file from Mike Denly’s webpage. It is a report on governance in Armenia that Mike Denly and Mike Findley prepared for the US Agency for InternationalDevelopment (USAID). [5 points]

```{r}

#install.packages('topicmodels')
library(pdftools)
library(tidyr)
library(tidytext)
library(dplyr)
library(stringr)
library(ggplot2)

#load the pdf file
armeniatext = pdf_text(pdf = "https://pdf.usaid.gov/pdf_docs/PA00TNMG.pdf")

# armeniatext is a character vector
armeniatext
```


12. Convert the text pulled from this .pdf file to a data frame, using the ,
stringsAsFactors=FALSE option. Call the data frame armeniatext. [5 points]

```{r}
# turn the text into a data frame where each row is a page of text
armeniatext=as.data.frame(armeniatext, stringsAsFactors = FALSE)
armeniatext$page=c(1:65)
colnames(armeniatext)[which(names(armeniatext) == "armeniatext")] <- "text"
```


13. Tokenize the data by word and then remove stop words. [5 points]
```{r}

#in order to tokenize text into words:
armeniatext = armeniatext %>%
  unnest_tokens(word, text)

#in order to get rid of stop words:
data(stop_words)
armeniatext <- armeniatext %>%
  anti_join(stop_words)
```


14. Figure out the top 5 most used word in the report. [5 points]

```{r}
#word frequencies
freq <- armeniatext %>%
count(word, sort = TRUE)

head(freq)
```


15.Load the Billboard Hot 100 webpage, which we explored in the course modules. Name the list object:hot100exam [5 points]

```{r}
library(rvest)
library(dplyr)

# load the billboard hot 100 chart
hot100page <- "https://www.billboard.com/charts/hot-100"
hot100exam <- read_html(hot100page)

hot100exam
str(hot100exam)


```


16. Use rvest to obtain identify all of the nodes in the webpage. [5 points]

```{r}
# declare the full structure of the webpage to R
body_nodes <- hot100exam %>%
  html_node("body") %>%
  html_children()
body_nodes

body_nodes %>%
  html_children()
  
```


17.Use Google Chrome developer to identify the necessary tags and pull the data on Rank,Artist,Title, and Last Week. 

```{r}
# pull out specific data from the webpage.
# rank, artist, title

rank <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
'chart-element__rank__number')]") %>%
  rvest::html_text()

artist <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
'chart-element__information__artist')]") %>%
  rvest::html_text()

title <- hot100exam %>%
  rvest::html_nodes('body') %>%
  xml2::xml_find_all("//span[contains(@class,
'chart-element__information__song')]") %>%
  rvest::html_text()

last_week <- hot100exam %>%
rvest::html_nodes('body') %>%
xml2::xml_find_all("//span[contains(@class,
'chart-element__information__delta__text text--last')]") %>%
  rvest::html_text()

# combine them 
chart_df <- data.frame(rank, artist, title, last_week)
knitr::kable(
  chart_df %>% head(10))

View(chart_df)
```


Final question. Save all of the files (i.e. .Rmd, .dta, .pdf/Word Doc), push them to your
GitHub repo, and provide us with the link to that repo.

Git hup repo: https://github.com/taeyoung-lee/exam3